Exploration of clustering results

### 2024-08-09 analyses/cell-type-wilms-tumor-06/notebook-template/01-clustering.Rmd
Update analyses/cell-type-wilms-tumor-06/notebook-template/01-clustering.Rmd
Co-authored-by: Stephanie Spielman <stephanie.spielman@gmail.com>

---
title: "Evaluation of clustering parameters"
author: maud-p
date: '`r format(Sys.time(), "%B %d, %Y %H:%M:%S %Z")`'
output:
  html_document: 
    toc: yes
    toc_float: yes
    code_folding: hide
    highlight: pygments
    df_print: kable
params:
  sample_name: ~
  sample_path: ~
  out_rds_path: ~
---

>>>>

---
title: "Exploration of clustering results"
author: maud-p
date: '`r format(Sys.time(), "%B %d, %Y %H:%M:%S %Z")`'
output:
  html_document: 
    toc: yes
    toc_float: yes
    code_folding: hide
    highlight: pygments
    df_print: kable
params:
  sample_name: ~
  sample_path: ~
  out_rds_path: ~
---
